---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# strongr

<!-- badges: start -->
[![R-CMD-check](https://github.com/kdschneider/strongr/actions/workflows/r-check-standard.yaml/badge.svg)](https://github.com/kdschneider/strongr/actions/workflows/r-check-standard.yaml)
<!-- badges: end -->

> This package is very much work in progress!

## Overview

The goal of strongr is to allow easy creation of workout-plans and logging of progress.

As of now the planned functions are:

  - `create_plan()`: Create a workout-plan from a set of input parameters and/or workouts.
  - `create_workout()`: Create a specific workout. One or more workouts  can be used to create a plan.
  - `add_training()`: Add a training session to the workout-plan. You should be able to specifiy if a set was failed. 
  - `get_next_training()`: Get weights (maybe with warmup weights) for the next training session. 
  - `deload()`: Failed `x` sets in a row? Time to face the truth and deload...
  
## Installation

```{r eval = FALSE}
# Install the development version from GitHub:
# install.packages("devtools")
devtools::install_github("kdschneider/strongr")
```

## Usage

`no use as of now, just garbage...`
